Digital History in Finland, 1488-1828

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok

```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {

@@

@@

theme_set(theme_bw(20))
p <- ggplot(dfs, aes(x = publication_decade, y = n)) +
       geom_point(size = 5) +
       geom_line() +       
       xlab("Publication year") +
       ylab("Title count (n)") +
       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))       
print(p)

@@

theme_set(theme_bw(20))
p <- ggplot(dfs, aes(x = publication_decade, y = paper)) +
       geom_point(size = 5) +
       geom_line() +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))
print(p)

>>>>

```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {

@@

df <- dfl %>% group_by(publication_year, language) %>%
             summarise(n = n(),
	               paper = sum(paper.consumption.km2, na.rm = TRUE))

@@

theme_set(theme_bw(20))
p <- ggplot(dfs, aes(x = publication_year, y = n)) +
       geom_point(size = 2) +
       #geom_line() +
       geom_smooth(col = "black") +              
       xlab("Publication year") +
       ylab("Title count (n)") +
       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))       
print(p)

@@

theme_set(theme_bw(20))
p <- ggplot(dfs, aes(x = publication_year, y = paper)) +
       geom_point(size = 2) +
       #geom_line() +
       geom_smooth(col = "black") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))
print(p)
